The \project{UNRAVE} catalog

### 2016-08-12 article/unrave.tex

%\begin{figure}[p]
%\caption{A H-R diagram showing the training set labels.\label{fig:training-set-hrd}}
%\end{figure}

%\begin{figure}[p]
%\caption{A H-R diagram showing the test set labels.\label{fig:test-set-hrd}}
%\end{figure}

%\begin{figure}[p]
%\caption{Stellar label comparison between the \project{UNRAVE} catalog and the \project{RAVE} fourth data release.\label{fig:dr4-comparison}}
%\end{figure}

%\begin{figure}[p]
%\caption{Stellar label comparison between the \project{UNRAVE} catalog and the \project{RAVE} fourth data release.\label{fig:dr4-comparison}}
%\end{figure}

>>>>

\begin{figure}[p]
\caption{A H-R diagram showing the training set labels.\label{fig:training-set-hrd}}
\end{figure}

\begin{figure}[p]
\caption{A H-R diagram showing the test set labels.\label{fig:test-set-hrd}}
\end{figure}

\begin{figure}[p]
\caption{The RMS of the test set labels as a function of S/N ratio for repeated stars in the test set.\label{fig:test-set-repeats}}
\end{figure}

\begin{figure}[p]
\caption{Stellar label comparison between the \project{UNRAVE} catalog and the \project{RAVE} fourth data release.\label{fig:dr4-comparison}}
\end{figure}

\begin{figure}[p]
\caption{Stellar label comparison between the \project{UNRAVE} catalog and the \project{Gaia-ESO Survey} fourth internal data release.\label{fig:dr4-comparison}}
\end{figure}

\begin{figure}[p]
\caption{Stellar label comparisons between the \project{UNRAVE} catalog and the samples discussed in \citep{kordopatis_2014}}
\end{figure}
